Initial estuarine response to the nutrient dense Piney Point wastewater discharge into Tampa Bay, Florida

### 2021-10-07 manu-draft.Rmd
update seagrass macro fo plot

```{r trnfrq, fig.cap = paste0('Frequency occurrence estimates for (a) area 1 and (b) area 3 (Figure \\@ref(fig:map)a) for seagrass (top) and macroalgae (bottom) rapid response transect surveys across all transects (n = ', ntrnscnt, ') near Piney Point.  Estimates are grouped by sample months in 2021. Frequency occurrences are absolute for each taxa based on presence/absence.')}
knitr::include_graphics(here('figs/trnfrq.jpeg'))
```

>>>>

```{r trnfrq, fig.cap = paste0('Frequency occurrence estimates for (a) area 1 and (b) area 3 (Figure \\@ref(fig:map)a) for seagrass (top) and macroalgae (bottom) rapid response transect surveys across all transects (n = ', ntrnscnt, ') near Piney Point.  Estimates are grouped by sample months in 2021. Frequency occurrences are absolute for each taxa based on presence/absence, whereas the total frequency occurrence applies to any taxa observed on each transect.')}
knitr::include_graphics(here('figs/trnfrq.jpeg'))
```
